### 2013-03-28 doc/sosp13/intro.tex
ni

We believe we can support irregular applications with good performance and
cost-effectiveness with commodity hardware for two main reasons. First,
commodity multicore processors have become extremely fast with high clock
rates, large caches and robust DRAM bandwidth. So with careful software
engineering we can multiplex hundred of thousands of workers into a single
core. Second, commodity networks offer high bandwidth as long as messages are
large enough. Therefore with enough data requests in flight simultaneously,
the system can aggregate small messages into large enough ones.

We build on these two observations and develop \Grappa, a software runtime
system that allows a commodity cluster of x86-based nodes connected via an
InfiniBand network to be programmed as if it were a single, large,
shared-memory NUMA (non-uniform memory access) machine with scalable
performance for irregular applications. \Grappa tolerates communication
latencies with lightweight user-level tasking layer that supports a context
switch in as little as 38ns and can sustain a large number of active workers.
It bridges the commodity network bandwidth gap with a communication layer that
combines short messages originating from a large number of active workers
into larger ones.

>>>>

We believe we can support irregular applications with good performance and cost-effectiveness with commodity hardware for two main reasons. First, commodity multicore processors have become extremely fast with high clock rates, large caches and robust DRAM bandwidth. Second, commodity networks offer high bandwidth as long as messages are large enough. We build on these two observations and develop \Grappa, a software runtime system that allows a commodity cluster of x86-based nodes connected via an InfiniBand network to be programmed as if it were a single, large, shared-memory NUMA (non-uniform memory access) machine with scalable performance for irregular applications. \Grappa exploits fast processors and the memory hierarchy to provide a lightweight user-level tasking layer that supports a context switch in as little as 38ns and can sustain a large number of active workers. It bridges the commodity network bandwidth gap with a communication layer that combines short messages originating from a large number of active workers into larger ones.
